---
title: "Exploring the Shadows of Terror: The Influence of Terrorism on Public Opinion and Democratic Values"
author: 
  - Sinan Ma
  - Yuean Wang
  - Yang Zhou
thanks: "Code and data are available at: https://github.com/Sinanma/Terrorism_And_Citizens-_Political_Attitudes. Replication on Social Science Reproduction platform available at: "
date: today
date-format: long
abstract: "In an era where terrorism intersects with global politics, understanding its repercussions on public attitudes towards democracy is crucial. This paper replicates and extends the data analysis of effects of terrorism on public political opinion, considers various expressions of terrorism and a variety of research methodologies by analyzing findings from previous research. Our findings indicate that terrorism leads to an increase in outgroup hostility and a shift towards political conservatism, and observes variations in rally-'round-the-flag effects. These reactions are influenced by the nature of the terrorist threat and the sociopolitical context. Through this exploration, this paper contributes to the ongoing discourse on the implications of terrorism for democratic societies."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| 
library(tidyverse)
library(readxl) # reading excel files
library(ggplot2)
library(ggpubr) # for gg rearrange
library(dplyr)
```


# Introduction

As we entered the 21st century, terrorism has emerged as a central concern in global politics, influencing international relations and shaping the societal landscape across the world. This phenomenon has not only reshaped diplomatic engagements but also transformed societal dynamics on a global scale which prompts a critical examination of terrorism's broader implications, particularly its impact on public attitudes towards democracy. In an with regular occurrence of terrorist incidents, the impact of terrorism on public opinion has emerged as a critical area of research, bringing up attention to how incidents of terrorism reshape public attitudes towards outgroup hostility, political conservatism, and national unity.

Building upon this foundation, our study aims to replicate and extend the analysis by *Amélie Godefroidt* in 2022, published in American Journal of Political Science [@Godefroidt202], which highlighted the significant impact of various forms of terrorism on public attitudes, from local insurgencies to global campaigns.

This paper delves into the complex dynamics of terrorism's influence on public political opinion. It extends the discourse beyond conventional analysis to explore how various expressions of terrorism—ranging from domestic to international incidents—affect public attitudes, with a particular focus on outgroup hostility, political conservatism, and rally-'round-the-flag phenomena. Despite a growing body of research in this field, there remains a significant gap in understanding the holistic and nuanced effects of different forms of terrorism across diverse sociopolitical contexts. To address this gap, we systematically analyze and integrate findings from prior research, employing a variety of methodological approaches to offer a comprehensive overview of terrorism's impact on public sentiment.

Our investigation reveals that terrorism indeed prompts significant shifts in public opinion, leading to an increase in outgroup hostility and a tilt towards political conservatism, alongside observable variations in national unity rallying effects. These reactions are found to be deeply influenced by the nature of the terrorist threat and the specific sociopolitical context in which they occur. The findings underscore the critical role of context in shaping public responses to terrorism, highlighting the importance of considering the diversity of terrorism expressions and the sociopolitical landscape when evaluating its impact.

This research contributes to the ongoing dialogue on the implications of terrorism for democratic societies by providing empirical evidence of terrorism's subtle yet significant influence on public political attitudes. By shedding light on the conditions under which terrorism most profoundly affects public sentiment, this paper aims to inform policymakers and scholars alike, guiding the development of strategies that bolster democratic resilience in the face of terror. This paper is organized as follows: an overview of the methodological framework used in our analysis, a presentation of the findings, a discussion contextualizing these results within the broader implications for democracy, and concluding remarks that suggest directions for future research and policy considerations.

\newpage

# Data {#sec-data}

## Source
Our study is based on a detailed examination by Amélie Godefroidt published in 2022 in the American Journal of Political Science. This important research looks into how terrorism affects what people think about democracy and politics, using a wide range of examples from small local attacks to large international ones. We aim to do more research based on Godefroidt's work, using her collection of data from 241 papers, which cover 326 studies and provide 1,733 measurements of how terrorism influences people's political views. This collection of information, gathered through careful research and organization, is the main resource for our study as we explore the complex effects of terrorism in different settings around the world.

## Methodology
Our approach to expanding on the original study involves a detailed process known as meta-analysis. This means we take a closer look at a bunch of studies already done on how terrorism changes people's opinions and combine their results to get a clearer picture. Following the steps outlined by Godefroidt, we gather, sort out, and examine data from various sources, focusing on 1,733 data points that show the relationship between terrorism and public opinion. We make sure all these points can be compared fairly by converting them into a standard format and adjusting them so they all point in the same direction. This makes our analysis strong and trustworthy. We also add new studies to the mix and use more sophisticated statistical methods to handle the data better, aiming to deepen our understanding of terrorism's impact on how people feel about democracy, strangers, and political beliefs in different parts of the world.

We used the following functions: [@readxl], [@ggplot2], [@ggpubr], [@dplyr] in [@citeR] to create figure and analyze data.

\newpage
# Results

Our analysis, visualized in @fig-terrorism-trend, presents a multifaceted view of terrorism studies over the last three and a half decades.

Temporal Trends in Data Collection and Publication
Panel A: The Year of Data Collection indicates a notable increase in studies on terrorism following significant global events, such as the 9/11 attacks and the rise of the Islamic State (IS). These pivotal moments appear to catalyze research interest, suggesting a reactive pattern in the academic community to explore terrorism's societal effects following high-profile incidents.

Panel B: Corroborating this trend, the Year of Publication shows a parallel surge in scholarly outputs, with peaks also corresponding to the aftermath of major terrorist events. The data implies that not only does the occurrence of terrorism prompt more research but also hastens the dissemination of findings, potentially reflecting an urgent need to understand and address the immediate impacts of these events.

Variability in Terrorism Measures
Panel C: The Terrorism Measures graph illustrates the diversity of metrics used to gauge terrorism's impact. Acts of violence and threat exposure are the most commonly studied, indicating a research emphasis on direct experiences and perceptions of terrorism. Meanwhile, measures of fear and anger, while less frequent, point to an emerging interest in the affective responses terrorism elicits.

Diversity in Types of Terrorism Studied
Panel D: The Type of Terrorism chart reveals an overwhelming focus on Islamist terrorism, overshadowing other ideologies and forms of terrorism. This skew suggests a potential blind spot in the literature, where state terror and extreme-right terrorism are relatively underexamined, despite their significance in certain regions and contexts.

```{r fig.width=15, fig.height=16}
#| label: fig-terrorism-trend
#| fig-cap: Summary of Data Included in theMeta-Analysis
#| echo: false
#| warning: false
#| message: false

# make sure the PATH is right in your setup
# since paper.qmd is under outputs/paper/ folder, we have to jump to parent dir twice
PATH = "../../inputs/data/02-metaanalysis-data.xlsx"


dat <- read_excel(PATH, sheet = "Data",  col_names = TRUE, skip = 3)
dat_studies <- dat[c(1:87)] #studies.
dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)

### dataframe of reports
dat_reports <- dat[c(1:87)] #reports/publications.
dat_reports <- group_by(dat_reports, ID_R) %>% slice(1)


### set wished layout settings
mytheme <- theme(plot.title = element_text(face = "bold", size = (22), colour = "black"), 
                 axis.text = element_text(size = (18), colour = "black"),
                 axis.ticks.length = unit(0.5, "cm"),
                 axis.title.y = element_text(size = (22), colour = "black"),
                 axis.title.x = element_text(size = (22), colour = "white"))


# Figure 2A
StudyYear <- ggplot(dat_studies, aes(x=StudyYear)) + 
  geom_histogram(binwidth=1,
                 color="#000000", fill="#939598") +
  labs(x="to fill some space", y = "", title = "Year of Data Collection") +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
  theme_classic() #histogram year of study 
StudyYear <- StudyYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
StudyYear <- StudyYear + geom_vline(xintercept=2004, linetype="dashed", size = 1) #add line
StudyYear <- StudyYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS line
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2001, y=27, label = "9/11"),
                                    size=8) #add 9/11 label
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2007, y=35, label = "Madrid & \n Israel-Palestine"),
                                    size=6) #add label
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2014, y=44, label = "IS Attacks"),
                                    size=8) #add ISIS label
StudyYear <- StudyYear + mytheme

## Figure 2B
PubYear <- ggplot(dat_reports, aes(x=Year)) + 
  geom_histogram(binwidth=1, 
                 color="#000000", fill="#939598") +
  labs(title ="Year of Publication", x = "to fill some space", y = "") +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
  theme_classic() #histogram year of study 
PubYear <- PubYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
PubYear <- PubYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS France line
PubYear <- PubYear + geom_label(data = dat_reports,
                                aes(x=2001, y=27, label = "9/11"),
                                size=8) #add 9/11 label
PubYear <- PubYear + geom_label(data = dat_reports, 
                                aes(x=2014, y=44, label = "IS Attacks"),
                                size=8) #add ISIS label
PubYear <- PubYear + mytheme

# wrangling
dat$TerrorMeasure[dat$IV_Code==1] <- "Acts of violence"
dat$TerrorMeasure[dat$IV_Code==2] <- "Acts of violence"
dat$TerrorMeasure[dat$IV_Code==3] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==4] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==5] <- "Other"
dat$TerrorMeasure[dat$IV_Code==6] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==7] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==8] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==9] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==10] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==11] <- "Fear"
dat$TerrorMeasure[dat$IV_Code==12] <- "Anger"
dat$TerrorMeasure[dat$IV_Code==13] <- "Other"
dat$TerrorMeasure[dat$IV_Code==14] <- "Other"
dat$TerrorMeasure[dat$IV_Code==15] <- "Other"
dat$TerrorMeasure[dat$IV_Code==16] <- "Other"

dat$TerrorMeasure <- as.factor(dat$TerrorMeasure)

#visualization: Figure 2C
tmdat <- data.frame(prop.table(table(dat$TerrorMeasure)))
TerrorMeasures <- ggplot(tmdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
  geom_bar(stat="identity", width=0.7,
           color="#000000", fill="#939598") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0,.6),
                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
  labs(title = "Terrorism Measures", x="", y = "") +
  theme_classic() 
TerrorMeasures <- TerrorMeasures + mytheme

#wrangling
dat$TerrorType[dat$Type==0] <- "No ideology"
dat$TerrorType[dat$Type==1] <- "Islamist"
dat$TerrorType[dat$Type==2] <- "Extreme right"
dat$TerrorType[dat$Type==3] <- "Other"
dat$TerrorType[dat$Type==4] <- "Other"
dat$TerrorType[dat$Type==5] <- "State terror"
dat$TerrorType[dat$Type==6] <- "Other"
dat$TerrorType <- as.factor(dat$TerrorType)

#visualization: Figure 2D
ttdat <- data.frame(prop.table(table(dat$TerrorType)))
TerrorType <- ggplot(ttdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
  geom_bar(stat="identity", width=0.7,
           color="#000000", fill="#939598") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
  labs(title = "Type of Terrorism", x = "", y = "") +
  theme_classic() 
TerrorType <- TerrorType + mytheme


# jpeg("Fig2.jpeg", width = 15, height = 16, units = 'in', res = 300)
ggarrange(StudyYear, PubYear, 
          TerrorMeasures, TerrorType,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          font.label = list(size = 22, color = "black"),
          ncol = 2, nrow = 2) #arrange all plots
# dev.off() #safe picture in high resolution.

# 
# StudyYear <- StudyYear + theme(aspect.ratio = 1) + theme(axis.text.x = element_text(size = 5))
# PubYear <- PubYear + theme(aspect.ratio = 1) + theme(axis.text.x = element_text(size = 5))
# TerrorMeasures <- TerrorMeasures + theme(aspect.ratio = 1) + theme(axis.text.x = element_text(size = 5))
# TerrorType <- TerrorType + theme(aspect.ratio = 1) + theme(axis.text.x = element_text(size = 5))
# 
# # Combine the plots into a 2x2 grid
# combined_plot <- (StudyYear | PubYear) / 
#                  (TerrorMeasures | TerrorType)
# 
# # Save the combined plot
# # ggsave("combined_plot.png", combined_plot, width = 10, height = 10)
# combined_plot
```

\newpage

Diverse Reactions to Ideological Terrorism
Outgroup Hostility: Our analysis, represented in @fig-reactions-to-terrorism, underscores that while all forms of ideological terrorism lead to outgroup hostility, the response is strongest in the face of Islamist terrorism. This could reflect media portrayal and public perception biases, where Islamist acts are more closely associated with the concept of terrorism. Interestingly, other ideologies, or the absence of an ideological label, provoke less intense reactions, suggesting a nuanced public sensitivity to the context and framing of terrorist events.

Conservative Shift: A conservative shift in public opinion was noted across all ideological forms of terrorism, but it was less pronounced for 'No ideology' cases. This suggests that the presence of a clear ideological motive in terrorism might be a key driver in swaying public opinion towards conservative policies and viewpoints.

Impact of Research Design on Perceived Threat
Rally Effects: When examining the influence of research design, experimental designs showed a more marked rally effect compared to cross-sectional studies. This difference indicates that the controlled environment of an experiment, often simulating a direct terrorism threat, might amplify the unifying sentiment among the participants.

Influence of Sample and Country Specifics
General Population vs. Targeted Samples: The general population samples showed a more consistent increase in outgroup hostility and conservatism across the board, as opposed to student or convenience samples. This highlights the importance of sample representativeness in gauging the true pulse of public opinion in response to terrorism.

Geographic Variations: The country-specific analysis revealed that the United States and Israel, both countries with prolonged experiences of terrorism, showed stronger correlations across all three measures compared to other countries. This may be attributed to the higher frequency of terrorist incidents and the consequent heightened public awareness and reaction in these nations.

Guilt-by-Association Effects
Lastly, the 'Guilt-by-Association' section of @fig-reactions-to-terrorism provides an intriguing insight into how strong associations with terrorism significantly affect public attitudes, more so than moderate or no associations. This underscores the powerful role of narrative and association in shaping public sentiment post-terrorism.

We used the following additional functions: [@broom], [@dotwhisker], [@cowplot], [@metafor] in [@citeR] to create @fig-reactions-to-terrorism.

```{r}
#| echo: false
#| warning: false
#| message: false


##### Fig3A.1 Overall ##### 
library(broom)
library(dotwhisker)
library(cowplot)
library(metafor)
############################
# 1) outgroup dataset
dat_outgroup <- dat[dat$PA_Category == 10 |
                      dat$PA_Category == 99, ]
# 2) conservative shift dataset
dat_conservatism <- dat[dat$PA_Category == 5 |
                          dat$PA_Category == 6 |
                          dat$PA_Category == 7 |
                          dat$PA_Category == 8 |
                          dat$PA_Category == 9 |
                          dat$PA_Category == 11, ]
# 3) rally-around-the-flag dataset
dat_rally <- dat[dat$PA_Category == 1 |
                   dat$PA_Category == 2 |
                   dat$PA_Category == 3 |
                   dat$PA_Category == 4, ]
######################################################
dat_outgroup$TerrorType2[dat_outgroup$Type==0] <- "No ideology"
dat_outgroup$TerrorType2[dat_outgroup$Type==1] <- "Islamist"
dat_outgroup$TerrorType2[is.na(dat_outgroup$TerrorType2)] <- "Other"
dat_outgroup$TerrorType2 <- as.factor(dat_outgroup$TerrorType2)
#convert into dummy variables
dat_outgroup$Islam <- ifelse(dat_outgroup$TerrorType2=="Islamist", yes=1, no=0)
dat_outgroup$No_Ideology <- ifelse(dat_outgroup$TerrorType2=="No ideology", yes=1, no=0)
dat_outgroup$Other_Ideology <- ifelse(dat_outgroup$TerrorType2=="Other", yes=1, no=0)
################################
dat_outgroup$Exp <- ifelse(dat_outgroup$TypeStudy==1, yes=1, no=0)
dat_outgroup$QuasiLong <- ifelse(dat_outgroup$TypeStudy==2 | 
                                   dat_outgroup$TypeStudy==4, yes=1, no=0)
dat_outgroup$Corr <- ifelse(dat_outgroup$TypeStudy==3, yes=1, no=0)
################################
dat_outgroup$Sample[dat_outgroup$GeneralPop==1] <- "General"
dat_outgroup$Sample[dat_outgroup$StudentPop==1] <- "Student"
dat_outgroup$Sample[is.na(dat_outgroup$Sample)] <- "Convenience"
dat_outgroup$Sample <- as.factor(dat_outgroup$Sample)
dat_outgroup$General <- ifelse(dat_outgroup$Sample=="General", yes=1, no=0)
dat_outgroup$Student <- ifelse(dat_outgroup$Sample=="Student", yes=1, no=0)
dat_outgroup$Convenience <- ifelse(dat_outgroup$Sample=="Convenience", yes=1, no=0)
################################
dat_outgroup$US <- ifelse(dat_outgroup$Country=="US", yes=1, no=0)
dat_outgroup$Israel <- ifelse(dat_outgroup$Country=="Israel", yes=1, no=0)
dat_outgroup$Other_c <- ifelse(dat_outgroup$US==0 
                               & dat_outgroup$Israel==0, yes=1, no=0)
############################
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==2] <- "A lot"
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==1] <- "A bit"
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==0] <- "No"
dat_outgroup$TargetSim <- as.factor(dat_outgroup$TargetSim)
#convert into dummy variables
dat_outgroup$Lot <- ifelse(dat_outgroup$TargetSim=="A lot", yes=1, no=0)
dat_outgroup$Bit <- ifelse(dat_outgroup$TargetSim=="A bit", yes=1, no=0)
dat_outgroup$No <- ifelse(dat_outgroup$TargetSim=="No", yes=1, no=0)

########################################
dat_conservatism$TerrorType2[dat_conservatism$Type==0] <- "No ideology"
dat_conservatism$TerrorType2[dat_conservatism$Type==1] <- "Islamist"
dat_conservatism$TerrorType2[is.na(dat_conservatism$TerrorType2)] <- "Other"
dat_conservatism$TerrorType2 <- as.factor(dat_conservatism$TerrorType2)
#convert into dummy variables
dat_conservatism$Islam <- ifelse(dat_conservatism$TerrorType2=="Islamist", yes=1, no=0)
dat_conservatism$No_Ideology <- ifelse(dat_conservatism$TerrorType2=="No ideology", yes=1, no=0)
dat_conservatism$Other_Ideology <- ifelse(dat_conservatism$TerrorType2=="Other", yes=1, no=0)
#############################
dat_conservatism$Exposure <- ifelse(dat_conservatism$TerrorMeasure=="Acts of violence", yes=1, no=0)
dat_conservatism$R_Exposure <- ifelse(dat_conservatism$TerrorMeasure=="Reported exposure", yes=1, no=0)
dat_conservatism$Threat <- ifelse(dat_conservatism$TerrorMeasure=="Threat", yes=1, no=0)
dat_conservatism$Emotions <- ifelse(dat_conservatism$TerrorMeasure=="Fear" | 
                                      dat_conservatism$TerrorMeasure=="Anger", yes=1, no=0)
dat_conservatism$Fear <- ifelse(dat_conservatism$TerrorMeasure=="Fear", yes=1, no=0)
dat_conservatism$Anger <- ifelse(dat_conservatism$TerrorMeasure=="Anger", yes=1, no=0)
dat_conservatism$Other_IV <- ifelse(dat_conservatism$TerrorMeasure=="Other", yes=1, no=0)
################################################################
#recode data
dat_conservatism$Design[dat_conservatism$TypeStudy==1] <- "Experiments"
dat_conservatism$Design[dat_conservatism$TypeStudy==2] <- "Quasi-Long"
dat_conservatism$Design[dat_conservatism$TypeStudy==3] <- "Correlations"
dat_conservatism$Design[dat_conservatism$TypeStudy==4] <- "Quasi-Long"
dat_conservatism$Design <- as.factor(dat_conservatism$Design)
#convert characters into dummy variables
dat_conservatism$Exp <- ifelse(dat_conservatism$TypeStudy==1, yes=1, no=0)
dat_conservatism$QuasiLong <- ifelse(dat_conservatism$TypeStudy==2 | 
                                       dat_conservatism$TypeStudy==4, yes=1, no=0)
dat_conservatism$Corr <- ifelse(dat_conservatism$TypeStudy==3, yes=1, no=0)
################################################
#recode data
dat_conservatism$Country2[dat_conservatism$Country=="US"] <- "US"
dat_conservatism$Country2[dat_conservatism$Country=="Israel"] <- "Israel"
dat_conservatism$Country2[is.na(dat_conservatism$Country2)] <- "Other"
dat_conservatism$Country2 <- as.factor(dat_conservatism$Country2)
#convert characters into dummy variables
dat_conservatism$US <- ifelse(dat_conservatism$Country=="US", yes=1, no=0)
dat_conservatism$Israel <- ifelse(dat_conservatism$Country=="Israel", yes=1, no=0)
dat_conservatism$Other_c <- ifelse(dat_conservatism$US==0 
                               & dat_conservatism$Israel==0, yes=1, no=0)
################################################

#recode data
dat_conservatism$Sample[dat_conservatism$GeneralPop==1] <- "General"
dat_conservatism$Sample[dat_conservatism$StudentPop==1] <- "Student"
dat_conservatism$Sample[is.na(dat_conservatism$Sample)] <- "Convenience"
dat_conservatism$Sample <- as.factor(dat_conservatism$Sample)
#convert characters into dummy variables
dat_conservatism$General <- ifelse(dat_conservatism$Sample=="General", yes=1, no=0)
dat_conservatism$Student <- ifelse(dat_conservatism$Sample=="Student", yes=1, no=0)
dat_conservatism$Convenience <- ifelse(dat_conservatism$Sample=="Convenience", yes=1, no=0)

################################################
set.seed(1234)
og_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                     method = "ML")
og_overall_df <- tidy(og_overall) # create data.frame of regression results

og_overall_df <- og_overall_df %>%  #re-label variable
  relabel_predictors(overall = "Overall Fisher's Z \n Correlation Coef." )           
og_overall_plot <- dwplot(og_overall_df, #plot
                          dot_args = list(size = 3),
                          whisker_args = list(size = 1),
                          vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 1))+
  ggtitle("Outgroup Hostility") +
  scale_color_grey() +
  xlim(-0.1, .25) +
  theme(axis.title.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.text.y = element_text(face = "bold",size = 14),
        axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        panel.background = element_rect(fill = "grey90",
                                        colour = "grey90"),
        panel.grid = element_line(colour = "grey60"))


##### Fig3A.2 Terror type ##### 
#fit model and plot results
set.seed(1234)
og_terror <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Islam, Other_Ideology, No_Ideology),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_terror_df <- tidy(og_terror) # create data.frame of regression results

og_terror_df <- og_terror_df %>%  #re-label variable
  relabel_predictors(c(Islam = "Islamist",
                       Other_Ideology  = "Other ideology",
                       No_Ideology  = "No ideology"))
og_terror_plot <- dwplot(og_terror_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25) 

##### Fig3A.3 Research Design ##### 
#fit model and plot results
set.seed(1234)
og_design <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Exp, QuasiLong, Corr),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_design_df <- tidy(og_design) # create data.frame of regression results

og_design_df <- og_design_df %>%  #re-label variable
  relabel_predictors(c(Exp = "Experiment",
                       Corr  = "Cross-sectional",
                       QuasiLong  = "Other designs"))
og_design_plot <- dwplot(og_design_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25) 

##### Fig3A.4 Sample  ##### 
#fit model and plot results
set.seed(1234)
og_sample <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(General, Student, Convenience),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_sample_df <- tidy(og_sample) # create data.frame of regression results

og_sample_df <- og_sample_df %>%  #re-label variable
  relabel_predictors(c(General = "General population",
                       Student  = "Student sample",
                       Convenience  = "Convenience sample"))
og_sample_plot <- dwplot(og_sample_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25) 

##### Fig3A.5 Geography ##### 
#fit model and plot results
set.seed(1234)
og_location <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(US, Israel, Other_c),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")
og_location_df <- tidy(og_location) # create data.frame of regression results

og_location_df <- og_location_df %>%  #re-label variable
  relabel_predictors(c(US = "United States",
                       Israel  = "Israel",
                       Other_c  = "Other countries"))
og_location_plot <- dwplot(og_location_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25) 

##### Fig3A.6 Guilt-by-Association ##### 
#fit model and plot results
set.seed(1234)
og_association <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Lot, Bit, No),
                      intercept=F, 
                      random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                      method = "ML")

og_association_df <- tidy(og_association) # create data.frame of regression results

og_association_df <- og_association_df %>%  #re-label variable
  relabel_predictors(c(Lot = "Strong association",
                       Bit  = "Moderate association",
                       No  = "No association"))
og_association_plot <- dwplot(og_association_df, #plot
                           dot_args = list(size = 2),
                           whisker_args = list(size = 0.5),
                           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  ggtitle("Guilt-By-Association") +
  scale_y_discrete(position = "left") +
  scale_color_grey() +
  theme(axis.title=element_text(face = "bold"),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25) 

##### Fig3A Outgroup Hostility Effect Sizes Plot ##### 
og_plots <- plot_grid(og_overall_plot, og_terror_plot, og_design_plot, og_sample_plot, og_location_plot,
                      og_association_plot,
                      ncol=1, nrow=6, 
                      rel_heights=c(0.8,1,1,1,1,1), align = "v")


# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3B. Conservative Shift Hypothesis ##### 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3B.1 Overall ##### 
set.seed(1234)
cs_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                     method = "ML")
cs_overall_df <- tidy(cs_overall) # create data.frame of regression results

cs_overall_df <- cs_overall_df %>% 
  relabel_predictors(c(overall = "Overall Effect Size")) #re-label variable
cs_overall_plot <- dwplot(cs_overall_df, #plot
                          dot_args = list(size = 3),
                          whisker_args = list(size = 1),
                          vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 1))+
  ggtitle("Conservative Shift") +
  scale_color_grey() +
  xlim(-0.1, .25) +
  theme(axis.title.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.ticks=element_blank(),
        axis.text=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        panel.background = element_rect(fill = "grey90",
                                        colour = "grey90"),
        panel.grid = element_line(colour = "grey60"))

##### Fig3B.2 Terror type ##### 
#fit model and plot results
set.seed(1234)
cs_terror <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Islam, Other_Ideology, No_Ideology),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")

cs_terror_df <- tidy(cs_terror) # create data.frame of regression results

cs_terror_df <- cs_terror_df %>%  #re-label variable
  relabel_predictors(c(Islam = "Islamist",
                       Other_Ideology  = "Other Ideology",
                       No_Ideology  = "No Ideology"))
cs_terror_plot <- dwplot(cs_terror_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), axis.text=element_blank(), axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25) 

##### Fig3B.3 Research Design ##### 
#fit model and plot results
set.seed(1234)
cs_design <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Exp, QuasiLong, Corr),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")
cs_design_df <- tidy(cs_design) # create data.frame of regression results

cs_design_df <- cs_design_df %>%  #re-label variable
  relabel_predictors(c(Exp = "Experiments",
                       Corr  = "Cross-Sectional",
                       QuasiLong  = "Other Designs"))
cs_design_plot <- dwplot(cs_design_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), axis.text=element_blank(), 
        axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25) 

##### Fig3B.4 Sample  ##### 
#fit model and plot results
set.seed(1234)
cs_sample <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(General, Student, Convenience),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")

cs_sample_df <- tidy(cs_sample) # create data.frame of regression results

cs_sample_df <- cs_sample_df %>%  #re-label variable
  relabel_predictors(c(General = "General Population",
                       Student  = "Student Samples",
                       Convenience  = "Convenience Samples"))
cs_sample_plot <- dwplot(cs_sample_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), 
        axis.text=element_blank(), axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25) 

##### Fig3B.5 Geography ##### 
#fit model and plot results
set.seed(1234)
cs_location <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(US, Israel, Other_c),
                      intercept=F, 
                      random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                      method = "ML")
cs_location_df <- tidy(cs_location) # create data.frame of regression results

cs_location_df <- cs_location_df %>%  #re-label variable
  relabel_predictors(c(US = "United States",
                       Israel  = "Israel",
                       Other_c  = "Other Countries"))
cs_location_plot <- dwplot(cs_location_df, #plot
                           dot_args = list(size = 2),
                           whisker_args = list(size = 0.5),
                           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), 
        axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25) 

##### Fig3B Conservative Shift Effect Sizes Plot ##### 
cs_plots <- plot_grid(cs_overall_plot, cs_terror_plot, cs_design_plot, cs_sample_plot, cs_location_plot, 
                      ncol=1, nrow=6, 
                      rel_heights=c(0.8,1,1,1,1,1), align = "v")

```





```{r fig.width=15, fig.height=16}
#| label: fig-reactions-to-terrorism
#| fig-cap: Relationship between Terrorism and Political Attitudes Conditional on Substantive and Methodological Factors
#| echo: false
#| warning: false
#| message: false


# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3C. Rally Effects Hypothesis ##### 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3C.1 Overall ##### 
#recode data
dat_rally$TerrorType2[dat_rally$Type==0] <- "No ideology"
dat_rally$TerrorType2[dat_rally$Type==1] <- "Islamist"
dat_rally$TerrorType2[is.na(dat_rally$TerrorType2)] <- "Other"
dat_rally$TerrorType2 <- as.factor(dat_rally$TerrorType2)
#convert into dummy variables
dat_rally$Islam <- ifelse(dat_rally$TerrorType2=="Islamist", yes=1, no=0)
dat_rally$No_Ideology <- ifelse(dat_rally$TerrorType2=="No ideology", yes=1, no=0)
dat_rally$Other_Ideology <- ifelse(dat_rally$TerrorType2=="Other", yes=1, no=0)


####################################


#convert characters into dummy variables
dat_rally$Exposure <- ifelse(dat_rally$TerrorMeasure=="Acts of violence", yes=1, no=0)
dat_rally$R_Exposure <- ifelse(dat_rally$TerrorMeasure=="Reported exposure", yes=1, no=0)
dat_rally$Threat <- ifelse(dat_rally$TerrorMeasure=="Threat", yes=1, no=0)
dat_rally$Emotions <- ifelse(dat_rally$TerrorMeasure=="Fear" | 
                                      dat_rally$TerrorMeasure=="Anger", yes=1, no=0)
dat_rally$Fear <- ifelse(dat_rally$TerrorMeasure=="Fear", yes=1, no=0)
dat_rally$Anger <- ifelse(dat_rally$TerrorMeasure=="Anger", yes=1, no=0)
dat_rally$Other_IV <- ifelse(dat_rally$TerrorMeasure=="Other", yes=1, no=0)

############################

#recode data
dat_rally$Design[dat_rally$TypeStudy==1] <- "Experiments"
dat_rally$Design[dat_rally$TypeStudy==2] <- "Quasi-Long"
dat_rally$Design[dat_rally$TypeStudy==3] <- "Correlations"
dat_rally$Design[dat_rally$TypeStudy==4] <- "Quasi-Long"
dat_rally$Design <- as.factor(dat_rally$Design)
#convert characters into dummy variables
dat_rally$Exp <- ifelse(dat_rally$TypeStudy==1, yes=1, no=0)
dat_rally$QuasiLong <- ifelse(dat_rally$TypeStudy==2 | 
                                dat_rally$TypeStudy==4, yes=1, no=0)
dat_rally$Corr <- ifelse(dat_rally$TypeStudy==3, yes=1, no=0)


####################################

#recode data
dat_rally$Sample[dat_rally$GeneralPop==1] <- "General"
dat_rally$Sample[dat_rally$StudentPop==1] <- "Student"
dat_rally$Sample[is.na(dat_rally$Sample)] <- "Convenience"
dat_rally$Sample <- as.factor(dat_rally$Sample)
#convert characters into dummy variables
dat_rally$General <- ifelse(dat_rally$Sample=="General", yes=1, no=0)
dat_rally$Student <- ifelse(dat_rally$Sample=="Student", yes=1, no=0)
dat_rally$Convenience <- ifelse(dat_rally$Sample=="Convenience", yes=1, no=0)
####################################
#recode data
dat_rally$Country2[dat_rally$Country=="US"] <- "US"
dat_rally$Country2[dat_rally$Country=="Israel"] <- "Israel"
dat_rally$Country2[is.na(dat_rally$Country2)] <- "Other"
dat_rally$Country2 <- as.factor(dat_rally$Country2)
#convert characters into dummy variables
dat_rally$US <- ifelse(dat_rally$Country=="US", yes=1, no=0)
dat_rally$Israel <- ifelse(dat_rally$Country=="Israel", yes=1, no=0)
dat_rally$Other_c <- ifelse(dat_rally$US==0 
                                   & dat_rally$Israel==0, yes=1, no=0)
####################################

set.seed(1234)
rf_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                     method = "ML")
rf_overall_df <- tidy(rf_overall) # create data.frame of regression results

rf_overall_df <- rf_overall_df %>% 
  relabel_predictors(c(overall = "Overall Effect Size")) #re-label variable
rf_overall_plot <- dwplot(rf_overall_df, #plot
                          dot_args = list(size = 3),
                          whisker_args = list(size = 1),
                          vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 1))+
  ggtitle("Rally Effects") +
  scale_color_grey() +
  xlim(-0.1, .25) +
  theme(axis.title.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.ticks=element_blank(),
        axis.text=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        panel.background = element_rect(fill = "grey90",
                                        colour = "grey90"),
        panel.grid = element_line(colour = "grey60"))


##### Fig3C.2 Terror type ##### 
#fit model and plot results
set.seed(1234)
rf_terror <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Islam, Other_Ideology, No_Ideology),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                    method = "ML")
rf_terror_df <- tidy(rf_terror) # create data.frame of regression results

rf_terror_df <- rf_terror_df %>%  #re-label variable
  relabel_predictors(c(Islam = "Islamist",
                       Other_Ideology  = "Other Ideology",
                       No_Ideology  = "No Ideology"))
rf_terror_plot <- dwplot(rf_terror_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  ylab("Ideology") +
  scale_y_discrete(position = "right") +
  scale_color_grey() +
  theme(axis.text=element_blank(), axis.ticks=element_blank(), 
        axis.title.y=element_text(face = "bold", size = 14),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25) 


##### Fig3C.3 Research Design ##### 
#fit model and plot results
set.seed(1234)
rf_design <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Exp, QuasiLong, Corr),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                    method = "ML")
rf_design_df <- tidy(rf_design) # create data.frame of regression results

rf_design_df <- rf_design_df %>%  #re-label variable
  relabel_predictors(c(Exp = "Experiments",
                       Corr  = "Cross-Sectional",
                       QuasiLong  = "Other Designs"))
rf_design_plot <- dwplot(rf_design_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text=element_blank(), axis.ticks=element_blank())+
  ylab("Design") +
  scale_y_discrete(position = "right") +
  scale_color_grey() +
  theme(axis.text=element_blank(), axis.ticks=element_blank(), 
        axis.title.y=element_text(face = "bold", size = 14),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25) 

##### Fig3C.4 Sample  ##### 
#fit model and plot results
set.seed(1234)
rf_sample <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(General, Student, Convenience),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                    method = "ML")
rf_sample_df <- tidy(rf_sample) # create data.frame of regression results

rf_sample_df <- rf_sample_df %>%  #re-label variable
  relabel_predictors(c(General = "General Population",
                       Student  = "Student Samples",
                       Convenience  = "Convenience Samples"))
rf_sample_plot <- dwplot(rf_sample_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text=element_blank(), axis.ticks=element_blank())+
  ylab("Sample") +
  scale_y_discrete(position = "right") +
  scale_color_grey() +
  theme(axis.text=element_blank(), axis.ticks=element_blank(), 
        axis.title.y=element_text(face = "bold", size = 14),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25) 


##### Fig3C.5 Geography ##### 
#fit model and plot results
set.seed(1234)
rf_location <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(US, Israel, Other_c),
                      intercept=F, 
                      random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                      method = "ML")
rf_location_df <- tidy(rf_location) # create data.frame of regression results

rf_location_df <- rf_location_df %>%  #re-label variable
  relabel_predictors(c(US = "United States",
                       Israel  = "Israel",
                       Other_c  = "Other Countries"))
rf_location_plot <- dwplot(rf_location_df, #plot
                           dot_args = list(size = 2),
                           whisker_args = list(size = 0.5),
                           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  ylab("Country") +
  scale_y_discrete(position = "right") +
  scale_color_grey() +
  theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), 
        axis.title.y=element_text(face = "bold", size = 14),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25) 

##### Fig3C Rally Effects Effect Sizes Plot ##### 
rf_plots <- plot_grid(rf_overall_plot, rf_terror_plot, rf_design_plot, rf_sample_plot, rf_location_plot,
                      ncol=1, nrow=6, 
                      rel_heights=c(0.8,1,1,1,1,1), align = "v")


# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
################################# FIGURE 3 ###############################
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 

ggarrange(og_plots, cs_plots, rf_plots,
          align = "hv",
          ncol = 3, nrow = 1,
          widths=c(2.2,1.3,1.4)) #arrange all plots

```
\newpage

# Discussion

Investigation of terrorism’s effects through public attitudes towards politics is a necessity so that to detect the social reaction to such thought-provoking disasters. Starting from Amélie Godefroidt’s pioneering study (Godefroidt, 2023), this paper takes further her insights and tries to bring in more deterministic factors that may work towards shaping the public opinion related to terrorism. However, both Mia and I agree on the implications of ethic, limitations and future hopeful prospects.

## Findings

Our research proves to be only an addition to Godefroidt's theory, however our findings, obviously, point to direct effects of the terrorist acts on citizens' political attitudes. One striking feature here is that of hatred for the out-group members and political conservatism of the prublic following such catastrophies. This affirms that terror creates a feeling of insecurity and a need for JWen safety which is a reason for a more cautious political position. Also, our results put the emphasis on the way terrorism is shaped in influence of terrorism. For instance, ideological violence perpetrated in the name of Islam seems to have a tremendous amplifying impact and induces much stronger responses than violence underpinned by other ideologies. This in accord with former studies focusing on the specific consequences of Islamist extremism on Western countries that associate the latter with the idea of cultural and national identity. Thus it is considered as a threat to the civic and national identity.

## Ethical Implications and Bias

Studying terrorism from the ethical dimension proves it cannot be underestimated. Being the such consequence causing sensitive part of the topic, and its role for evoking and spreading fear and xenophobia, the scientists should handle it with specific techniques. An application of rigorous meta-analysis methodology assures reliable inquiry, lack of harm, and the polysemic exploration of the problem of the correlation between terrorism and political attitudes. Nevertheless, it should be acknowledged that the existence of bias is one of the key challenges that could be connected with the initial studies in our analysis. For an example, each victim is likely to be bombarded over the media and end up being Islamist terrorism which is highly visible in media coverage and public discourse. Albeit, while one dimension of ideological violence may not be accurately portrayed, other forms such as far-right extremism or eco-terrorism may not be sufficiently emphasized. Such dyads are likely to find themselves in a arena in which distorted views will dominate and the situation will be perceived far from its true scale.

## Limitations

In addition to the implemented design in order to realize the highest accuracy of a meta-analysis, we faced several limitations, limiting the range and generality of our findings. Our approach which heavily depends on a secondary data is unable to control for all the conﬂounding variables that may be influential, such as socio-economic class or psychological characteristics of the individual. Furthermore, the use of published sources may leave room for the ‘file drawer’ effect wherein studies with positive results are likely to be published while studies with no significant effect are simply left in the drawer.

## Future Research

In order to rectify these limitations as well as bring clarity into how terrorism changes the political views of a society, there should be an all round approach for the research. At first, applying primary data collection methods, e.g. surveys or interviews, is a good idea since it can bring you concrete views of how people behave in terrible situations. This will ultimately allow the scientists to enable the research system to explore intricacies and contextual factors which may not be available in the datasets that currently exist. In addition, the issue must be viewed from a wider angle, not being limited only to a single terrorist ideology but covering the broad spectrum of ideologies. Our primary target however revolves around Islamist terrorism alone, yet the other extreme movements for instance, right- or left-wing extremism also deserve attention. It is critical for the success of counterterrorism policies and social unity that the concerns are comprehensively analyzed re the ideologies that shape the views of the mass public and the political attitudes. Moreover, as terrorism is seen in many contexts other than the Western world, exploring this issue will contribute to a deeper global comprehension. Terrorism being a very much issues based on the diversity of cultures, societies and their political emotions is not the same across the world. Years long longitudinal studies which track individuals perceptions overtime will provide a wealth of information to the long term effects of terrorism, to name some of these as a mention, radicalization, resilience and social transformation.

## Conclusion

In conclusion,, the work offer a new insight into what the influence of terrorism on political attitudes was in the past. Our research replicates Godefroidt's study while trying to expand on it. This is to drive home the fact that terrorists are always a constant factor in the society with their potentially dangerous ideologies. Furthermore, there is the endless ethical and biases topic which is very sensitive and proposing lanes for future research for the same problem is well thought out.

\newpage


# References
